---
title: "WP2 Example"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
```
```{r code0}
library(ggplot2)
library(dplyr)
install.packages("hockeystick")
library(hockeystick)
co2 <- get_carbon()
```
```{r code1}
ggplot(co2, aes(x = year, y = average)) + 
  geom_point(col = "red")+
  theme_bw()+
  labs(x = "Year", y = "Average Monthly Carbon Dioxoide (ppm)")
```

Figure 1. The rapid change in monthly averages of carbon dioxide as measured on Mauna Loa since 1958. Data was pulled from the `hockeystick` package on R and remains unchanged and unfiltered. Y axis shows parts per million. 

\newpage

```{r code2}
co3 <- co2 %>% filter(year>1980) 
ggplot(co3, aes(x = year, y = average)) + 
  geom_line(col = "yellow")+
  theme_bw()+
  labs(x = "") +
  labs(y = "parts.per.mil")+
  scale_y_continuous(limits = c(0, 400))+ 
  scale_x_continuous(n.breaks = 30)+
  labs(title = "Figure 2. The slow change in mon avg since 1958. 
       \n Data was pulled \nfrom the hockeystick package  
       and remains unchanged and unfiltered. Y axis shows parts per million.")
```


\newpage

# Code Used To Make These Plots
Below are the code chunks used to make these plots. Use **install.packages()** to install any missing packages before you run. 
      
```{r code0, eval=FALSE, echo=TRUE}
```

```{r code1, eval=FALSE, echo=TRUE}
```

```{r code2, eval=FALSE, echo=TRUE}
```
All of the Errors in Figure 2 (you don't need to call yours out in your submission, but you can if you like):

*  The caption says unfiltered, but the data is filtered. 
*  Caption also says since 1958 which is not true as it is filtered to 1980.
*  A line plot isn't a great choice here.
*  Yellow is virtually invisible.
*  The x axis has no label and is overlapping with too many breaks and no rotation.
*  The y axis has data artifacts and does not have a easy to read name
*  The y axis has too big of a scale, hides the trend.
*  The title is embedded in the figure. This R Markdown PDF still reads it okay but any other export would not have and it would have had anti aliasing issues.
*  The title is also erratic in spacing and is broken up in strange places.